---
title: "R for Data Science"
output: html_notebook
---

Vi skal lige have pakkerne i orden til brug. Primært tidyverse. Måske markdown. 

```{r include=FALSE}
pakker <- c("tidyverse", "rmarkdown")
lapply(pakker, require, character.only = TRUE)

```

```{r}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```


# A Graphing Template Excercises

1. Run ggplot(data = mpg). What do you see?

```{r}
ggplot(data = mpg)
```
Vi ser ikke det store! :)

2. How many rows are in mtcars? How many columns?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = mtcars))
```


3. What does the drv variable describe? Read the help for ?mpg to find out.

4. Make a scatterplot of hwy versus cyl.

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = cyl, y = hwy))
```


5. What happens if you make a scatterplot of class versus drv? Why is the plot not useful?

```{r}
ggplot2
```


2

3

4

5


Hvorfor viser den mon ikke nedenstående kode?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

```

Top
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))
```


